---
title: "ggOBI"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE
)
```

## Overview

This is my final project for the course SURV752 Data Vizualisation in the IPSDS program offered by the Universities of Mannheim and Maryland. 
The ```ggOBI``` package contains a ggplot2 theme for my favorite home improvement store OBI. So all the oranges and greys you can imagine and also a new take on an OBI color scheme, that my personal expert titled ```obi_autumn```.

## Installation

```{r install, eval=FALSE}
devtools::install_github("markusntz/ggOBI")
library(ggOBI)
```

For the full OBI experience it might be necessary to install also additional fonts (here Ubunutu), the following code should do the trick:

```{r load-extra-fonts, eval=FALSE}
install.packages("extrafont")
library(extrafont)
font_import()
loadfonts()
```

## Usage

You can use the package by adding the functions provided to your plots:

```{r example, message=FALSE}
library(ggplot2)
library(ggOBI) 
library(extrafont)

p <- ggplot(diamonds, aes(cut, fill = cut)) + 
  geom_bar() + 
  scale_fill_obi(palette = "obi_autumn") + 
  theme_obi()

p 
```
